### 2020-08-11 cases_and_policies/rmd/regressionsWithPlots.Rmd

sgtype <- opts_knit$get("rmarkdown.pandoc.to")
sgstyle <- 'default'
colors <-  scale_color_solarized
colors_fill <- scale_fill_solarized
rootdir <- system("git rev-parse --show-toplevel", intern=TRUE)[1]
rootdir <- "/Users/Hiro/Documents/GitHub/covid-impact" 
source(paste(rootdir,"cases_and_policies/R/exploratory.R", sep="/"))
source(paste(rootdir,"cases_and_policies/R/dataprep.R",sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/varlabels.R", sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/regprep.R", sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/generatetables.R", sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/bootstrap_felm.R", sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/rlassoPanel.R", sep="/"))
```

@@

cmat <-  cor(df[,c(bvars,pols,"pindex")], use="pairwise.complete.obs")
scmat <-
  matrix(sprintf("%.2f",cmat),nrow=(length(bvars)+length(pols)+1))

@@

yvar <- "dlogdd"
infovars <- list(c("dlogdd", "logdd"),
                  c("dlogdd", "logdd","dlogdd.national", "logdd.national")) 
L <- 21
sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
piy <- list() 
for (k in 1:length(infovars)) { 
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
  pols <- c("pmaskbus","pk12","pmovie","pshelter","prestaurant","pnonessential") 
  m <-  reg_fe(sdf, yvar, pols, NULL,
              sprintf("lag(%s, %d)", infovars[[k]], L), 0, L, "state + month")
  piy[[(1+4*(k-1))]] <- m
  m$reg$beta[1:(8+2*(k-1))] <- m$bc2[1:(8+2*(k-1))] 
  #m$reg$beta[1:(5+2*(k-1))] <- m$bc[1:(5+2*(k-1))] 
  # m$reg$tval <- m$reg$beta/m$reg$se
  # m$reg$pval <- pnorm(-abs(m$reg$beta), sd=m$reg$se)
  piy[[(2+4*(k-1))]] <- m
  pols <- c("pmaskbus","pk12","pindex") 
  #pols <- c("pmaskbus","pk12","pmovie","pindex") 
  m <-  reg_fe(sdf, yvar, pols, NULL,
              sprintf("lag(%s, %d)", infovars[[k]], L), 0, L, "state + month")
  piy[[(3+4*(k-1))]] <- m 
  m$reg$beta[1:(5+2*(k-1))] <- m$bc2[1:(5+2*(k-1))] 
  #m$reg$beta[1:(4+2*(k-1))] <- m$bc[1:(4+2*(k-1))] 
  # m$reg$tval <- m$reg$beta/m$reg$se
  # m$reg$pval <- pnorm(-abs(m$reg$beta), sd=m$reg$se) 
  piy[[(4+4*(k-1))]] <- m
}

colnames(piy[[1]]$reg$response) <- "dlogdd"  
showhtmltables(NULL, NULL,  piy); 
prefix="deaths-fe"
#savetextables(NULL, NULL, piy[1:4], prefix="cases-fe")
   ylbl <- colnames(piy[[1]]$reg$response)
    if (ylbl=="dlogdd") ylbl <- "Death Growth"
    if (ylbl=="dlogdc") ylbl <- "Case Growth"

## DML 
```{r regsdml, cache=FALSE, warning=FALSE, results='asis'}

library(glmnet)

@@

>>>>

sgtype <- opts_knit$get("rmarkdown.pandoc.to")
sgstyle <- 'default'
colors <-  scale_color_solarized
colors_fill <- scale_fill_solarized
rootdir <- system("git rev-parse --show-toplevel", intern=TRUE)[1]
source(paste(rootdir,"cases_and_policies/R/exploratory.R", sep="/"))
source(paste(rootdir,"cases_and_policies/R/dataprep.R",sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/varlabels.R", sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/regprep.R", sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/generatetables.R", sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/bootstrap_felm.R", sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/rlassoPanel.R", sep="/"))
```

@@

scmat <-
cmat <-  cor(df[,c(bvars,pols,"pindex")], use="pairwise.complete.obs")
  matrix(sprintf("%.2f",cmat),nrow=(length(bvars)+length(pols)+1))

@@

yvar <- "dlogdd"
infovars <- list(c("dlogdd", "logdd"),
                  c("dlogdd", "logdd","dlogdd.national", "logdd.national"))
L <- 21
sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
piy <- list()
for (k in 1:length(infovars)) {
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
  pols <- c("pmaskbus","pk12","pmovie","pshelter","prestaurant","pnonessential")
  m <-  reg_fe(sdf, yvar, pols, NULL,
              sprintf("lag(%s, %d)", infovars[[k]], L), 0, L, "state + month")
  piy[[(1+4*(k-1))]] <- m
  m$reg <- replacecoef(m$reg, m$bc2)
  piy[[(2+4*(k-1))]] <- m
  pols <- c("pmaskbus","pk12","pindex")
  m <-  reg_fe(sdf, yvar, pols, NULL,
              sprintf("lag(%s, %d)", infovars[[k]], L), 0, L, "state + month")
  piy[[(3+4*(k-1))]] <- m
  m$reg <- replacecoef(m$reg, m$bc2)
  piy[[(4+4*(k-1))]] <- m
}

colnames(piy[[1]]$reg$response) <- "dlogdd"
showhtmltables(NULL, NULL,  piy);
colnames(piy[[1]]$reg$response) <- "dlogdd"
showhtmltables(NULL, NULL,  piy);
#savetextables(NULL, NULL, piy[1:4], prefix="deaths-fe")
prefix <- "deaths-fe"
   ylbl <- colnames(piy[[1]]$reg$response)
    if (ylbl=="dlogdd") ylbl <- "Death Growth"
    if (ylbl=="dlogdc") ylbl <- "Case Growth"

    tbl <- capture.output(stargazer(
        lapply(piy[1:4], function(x) x$reg),
        type="latex",
        dep.var.labels.include=FALSE,
        title=ylbl,
        # omit=omit,
        # omit.labels=omit.labels,
        column.labels=c(yvar),
        column.separate=c(length(piy[1:4])),
        # add.lines=list(c("$\\sum_j \\mathrm{Policy}_j$",
        #                  sapply(piy, function(x) printstars(x$peff[1], x$peff[2]))),
        #                c("",
        #                  sprintf("(%.3f)",sapply(piy, function(x) x$peff[2])))
        #                ),
        omit.stat=c("f", "ser"), model.names=FALSE,
        no.space=TRUE,
        column.sep.width="1pt",
        df=FALSE, header=FALSE,
        model.numbers=TRUE))
    tbl <- relabel(tbl)
    tbl <- gsub("Model (\\d)", "\\(\\1\\)", tbl)
    #tbl <- gsub("No","Yes", tbl)
    texfile <- sprintf("%s/tex/tables_and_figures/%s-piy.tex",rootdir,prefix)
    cat(paste(tbl[c(-1,-2,-3,-4, -length(tbl))], collapse="\n"), file=texfile)
```

## DML

```{r regsdml, cache=FALSE, warning=FALSE, results='asis'}
library(glmnet)

@@

dreg <- function(x,d){ randomForest(x, d) } #ML method=Forest
yreg <- function(x,y){ randomForest(x, y) } #ML method=Forest
set.seed(1)
DML2.RF <- DML2.for.PLM(x, d, y, dreg, yreg, sdf, nfold=5)
set.seed(1)
DML2.RF <- DML2.for.PLM(x, d, y, dreg, yreg, sdf, nfold=10)
```
